---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gts v`r as.character(packageVersion("gts"))`

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

The goal of gts is to provide a `fable`-like interface to the `forecast` package.

## Installation

You can install the released version of `gts` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gts")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mtfairbanks/gts")
```
## Functions

`gts` has 4 core functions:

* `ts_prep()`: Convert a tsibble to a `gts` ready dataset
* `ts_model()`: Apply a `forecast` function
* `ts_forecast()`: Create forecasts for all trained models
* `ts_accuracy()`: Extract in-sample accuracy for all trained models

## Examples

We start by creating a tsibble object:

```{r message=FALSE}
library(gts)
library(tidyverse)
library(forecast)
library(tsibble)
library(tsibbledata)
library(janitor)

# Create tsibble
aus_ts <- tsibbledata::aus_production %>%
  pivot_longer(-Quarter, names_to = "product") %>%
  clean_names() %>%
  as_tsibble(index = quarter, key = product, value = value) %>%
  fill_gaps(value = 0)

aus_ts
```

You can now use this object to use `gts`:

```{r warning=FALSE}
# Create a mable-like tibble
aus_mbl <- aus_ts %>%
  ts_prep() %>%
  ts_model(forecast::ets) %>%
  ts_model(forecast::ets, with_log = TRUE, mode = "MAM") %>%
  ts_model(forecast::auto.arima, with_log = TRUE)

# Create a fable-like tibble
aus_fbl <- aus_mbl %>%
  ts_forecast(h = 4)

aus_fbl
```

You can also get in-sample accuracy:
```{r}
aus_mbl %>%
  ts_accuracy()
```
