---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

# gts v`r as.character(packageVersion("gts"))`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `gts` is to speed up the functionality provided by `fable`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("markfairbanks/gts")
```
## Functions

`gts` has 2 core functions:

* `ts_prep()`: Convert a data frame to a `gts` ready dataset
* `ts_split()`: Split your dataset to quickly enable parallel processing

## Examples

Starting with some example data:

```{r message=FALSE}
library(gts)
library(fpp3)
library(tidyverse)

aus_df <- tsibbledata::aus_livestock %>%
  rename_all(janitor::make_clean_names) %>%
  filter(state == "Australian Capital Territory") %>%
  mutate(month = as_date(month))

head(aus_df)
```

You can then use this to prep your data and create models

```{r}
aus_ts <- aus_df %>%
  ts_prep(key = c(animal, state), index = month, target = count) %>%
  mutate(mable = map(time_series, model,
                     ets = ETS(count)))
  
aus_ts
```

You can create forecasts from here, or get model accuracy.

```{r warning=FALSE}
aus_ts <- aus_ts %>%
  mutate(fable = map(mable, forecast, h = 1),
         accuracy = map(mable, accuracy))

aus_ts
```

You can unnest the fable as follows:

```{r}
aus_ts %>%
  ts_unnest_fable(fable, keep = c(animal, state))
```


## Running in parallel

```{r warning=FALSE}
pacman::p_load(furrr)

model_fn <- function(.data) {
  .data %>%
    mutate(mable = map(time_series, model,
                       ets = ETS(count)),
           fable = map(mable, forecast, h = 1),
           accuracy = map(mable, accuracy))
}

plan(multiprocess)

parallel_ts <- aus_df %>%
  ts_prep(key = c(animal, state), index = month, target = count) %>%
  ts_split(6) %>%
  future_map_dfr(model_fn)

future:::ClusterRegistry("stop")
```

