---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gts v`r as.character(packageVersion("gts"))`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of gts is to provide a `fable`-like interface to the `forecast` package.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("markfairbanks/gts")
```
## Functions

`gts` has 4 core functions:

* `ts_prep()`: Convert a tsibble to a `gts` ready dataset
* `ts_model()`: Apply a `forecast` function
* `ts_forecast()`: Create forecasts for all trained models
* `ts_accuracy()`: Extract in-sample accuracy for all trained models

## Examples

We start by creating a tsibble object:

```{r message=FALSE}
library(gts)

# # Create tsibble
# aus_ts <- tsibbledata::aus_production %>%
#   clean_names() %>%
#   pivot_longer(-quarter, names_to = "product") %>%
#   as_tsibble(index = quarter, key = product, value = value) %>%
#   fill_gaps(value = 0)
# 
# aus_ts
```

You can now use this tsibble to use `gts`:

```{r warning=FALSE}
# Create a mable-like tibble
# aus_mbl <- aus_ts %>%
#   ts_prep() %>%
#   ts_model(forecast::ets) %>%
#   ts_model(forecast::ets, with_log = TRUE, model = "MAM") %>%
#   ts_model(forecast::auto.arima, with_log = TRUE)
# 
# # Create a fable-like tibble
# aus_fbl <- aus_mbl %>%
#   ts_forecast(h = 4)
# 
# aus_fbl
```

You can also get in-sample accuracy:
```{r}
# aus_mbl %>%
#   ts_accuracy()
```


## Running in parallel

<!-- ```{r warning=FALSE} -->
<!-- pacman::p_load(furrr) -->

<!-- model_fn <- function(.ts) { -->
<!--   .ts %>% -->
<!--     ts_model(forecast::ets) %>% -->
<!--     ts_model(forecast::auto.arima) -->
<!-- } -->

<!-- plan(multiprocess) -->

<!-- tictoc::tic() -->

<!-- parallel_mbl <- aus_ts %>% -->
<!--   ts_prep() %>% -->
<!--   split(1:nrow(.) %% 6) %>% -->
<!--   future_map_dfr(model_fn) -->

<!-- inv_gc() -->

<!-- parallel_fbl <- parallel_mbl %>% -->
<!--   split(1:nrow(.) %% 6) %>% -->
<!--   future_map_dfr(ts_forecast) -->

<!-- tictoc::toc() -->

<!-- future:::ClusterRegistry("stop") -->
<!-- ``` -->

